Clause Size Reduction with \alluip Learning

### 2020-05-11 paper.tex
change wording for better format

\subsubsection{$\stablealluip$ in Modern SAT solvers.}
\begin{sloppypar}
To validate $\stablealluip$ as a practical learning scheme for modern
SAT solvers, we implemented $\stablealluip$ in the winners of 2017,
2018 and 2019 SAT Race
\cite{DBLP:conf/ijcai/LuoLXML17,ryvchin2018maple,Stepan2019MapleLCMDistChronoBT}
and in the $\expSAT$ \cite{MdSolimul2019expMalpe} ($\expSATShort$)
and $\cadical$~\cite{cadical} solver. $\expSATShort$ is a top ten solver from 2019 SAT race which
uses random walk simulation to help branching. We chose $\expSATShort$
because (1) it is one of the top solvers in the 2019 SAT Race that does
not use chronological backtracking; and (2) the random walk simulation
branching heuristic is different from local branching heuristic (VSIDS
and LRB) that we have considered in $\allUipAct$, $\allUipIn$, and
$\allUipEx$. We chose $\cadical$ because its default configuration\footnote{$\cadical$'s 
default configuration is different from the specialized 'sat' configuration, 
which solved the most SAT instances in the 2019 SAT Race.} (denote as $\defaultcadical$) 
solved 244 instances in the 2019 SAT Race, the highest among 
all participants. For this experimented, we used the latest available version of
 $\defaultcadical$ instead of the 2019 SAT Race participant~\cite{Armin2019Cadical}. 
  We compared these solver's base \oneuip learning scheme
with $\allUipPure$, $\allUipMin$ and the top two $\stablealluip$
variants, $\allUipAct$ and $\allUipIn$, on the SAT Race 2019 main
track benchmark. We report solved instances, PAR-2 score and the
average clause size.
\end{sloppypar}

@@

$\defaultcadical$ with \oneuip solved 249 instances,   
and $\allUipAct$ and $\allUipIn$ solved 2 and 3 more instance, respectively.  
The average learnt clause size of \oneuip on 
$\defaultcadical$ is much larger than other solvers' (101 vs 60) 
while the average clause size of $\stablealluip$ configurations are similar on all solvers.

>>>>

\subsubsection{$\stablealluip$ in Modern SAT solvers.}
\begin{sloppypar}
To validate $\stablealluip$ as a practical learning scheme for modern
SAT solvers, we implemented $\stablealluip$ in the winners of 2017,
2018 and 2019 SAT Race
\cite{DBLP:conf/ijcai/LuoLXML17,ryvchin2018maple,Stepan2019MapleLCMDistChronoBT}
and in the $\expSAT$ \cite{MdSolimul2019expMalpe} ($\expSATShort$)
and $\cadical$~\cite{cadical} solver. $\expSATShort$ is a top ten solver from 2019 SAT race which
uses random walk simulation to help branching. We chose $\expSATShort$
because (1) it is one of the top solvers in the 2019 SAT Race that does
not use chronological backtracking; and (2) the random walk simulation
branching heuristic is different from local branching heuristic (VSIDS
and LRB) that we have considered in $\allUipAct$, $\allUipIn$, and
$\allUipEx$. We chose $\cadical$ because its default configuration\footnote{$\cadical$'s 
default configuration is different from the specialized 'sat' configuration, 
which solved the most satisfiable instances in the 2019 SAT Race.} (denote as $\defaultcadical$) 
solved 244 instances in the 2019 SAT Race, the highest among 
all participants. For this experimented, we used the latest available version of
 $\defaultcadical$ instead of the 2019 SAT Race participant~\cite{Armin2019Cadical}. 
  We compared these solver's base \oneuip learning scheme
with $\allUipPure$, $\allUipMin$ and the top two $\stablealluip$
variants, $\allUipAct$ and $\allUipIn$, on the SAT Race 2019 main
track benchmark. We report solved instances, PAR-2 score and the
average clause size.
\end{sloppypar}

@@

$\defaultcadical$ with \oneuip solved 249 total instances. 
Applying $\allUipAct$ and $\allUipIn$ helped the solver solve 2 and 3 more instance, respectively.  
The average learnt clause size of \oneuip on 
$\defaultcadical$ is much larger than other solvers' (101 vs 60) 
while the average clause size of $\stablealluip$ configurations are similar on all solvers.
